COG-ED Manuscript

### 2021-11-16 06_Paper/COG-ED/Manuscript.Rmd
still not working

              pipelines_data[[i]] <-
                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & (pipelines_data[[i]]$rt < (pipemean + 2 * pipesd))
                                           & (pipelines_data[[i]]$rt > (pipemean - 2 * pipesd))) | (pipelines_data[[i]]$level != x), ]

@@

              pipelines_data[[i]] <-
                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & (pipelines_data[[i]]$rt < (pipemean + 3 * pipesd))
                                           & (pipelines_data[[i]]$rt > (pipemean - 3 * pipesd))) | (pipelines_data[[i]]$level != x), ]
            }
        }

>>>>

              pipelines_data[[i]] <-
                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & ((pipelines_data[[i]]$rt < (pipemean + 2 * pipesd))
                                           | (pipelines_data[[i]]$rt > (pipemean - 2 * pipesd)))) | (pipelines_data[[i]]$level != x), ]

@@

              pipelines_data[[i]] <-
                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & ((pipelines_data[[i]]$rt < (pipemean + 3 * pipesd))
                                           | (pipelines_data[[i]]$rt > (pipemean - 3 * pipesd)))) | (pipelines_data[[i]]$level != x), ]
            }
        }
